Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-09-14 paper.tex
Added code to generate timescale scatter plot
Added figure with duration spread and discussion

LBAs are a subset of galaxies from those in \citet{heckman05}.
\citet{heckman05} match galaxies detected in the \emph{GALEX} All-Sky Imaging
Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}
\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
and the radius is the half-light radius at 0.35$\,\micron$ ($u$-band);
(3) $z < 0.3$; and (4) no evidence for emission from an AGN.

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's instantaneous SFR has,
for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

@@

>>>>

LBAs are a subset of galaxies from those in \citet{heckman05}.
\citet{heckman05} match galaxies detected in the \emph{GALEX} All-Sky Imaging
Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}~
\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
and the radius is the half-light radius at 0.35$\,\micron$ ($u$-band);
(3) $z < 0.3$; and (4) no evidence for emission from an AGN.

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's instantaneous SFR has,
for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for three
reasons:
\begin{enumerate}
\item \citet{madau14} calculate conversion factors between luminosities and
star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.  They
assume a history of constant star formation rate to get factors as a function
the duration of a star formation episode.
\item \citet{madau14} use the models of \citet{conroy10} to calculate these
conversion factors.  The conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
using the conversion factor for a fixed UV escape fraction.
\item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
$L_{\mathrm{IR}}$ are valid at different durations of the star formation
episode.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{\label{spread}}
\end{figure}

@@

\bibitem[Conroy \& Gunn(2010)]{conroy10} Conroy, C., \& Gunn, J.~E.\ 2010, \apj,
712, 833
